\section{Future} \label{sec:future}

The core limitation to updating a visibility polygon of $O(v)$ size in
$O(1)$ time is that to actually observe the solution necessarily
requires $O(w)$ time to compute the window point intersections where
in the worst case $w \in O(v)$. Certainly then if the solution is
required frequently relative to the distance the visibility travels,
any dynamic visibility algorithm has a tight lower bound of
$\Omega(w)$.

\subsection{Practical Improvements} \label{sec:improvements}

Possibilities for making the \emph{UpdateVisibility} algorithm $\theta(1)$:
\begin{itemize}
\item Find the $k$ highest degree vertices in our precomputed Delaunay
graph. Since we do not actually care about the Delaunay properties, we
could find a way to retriangulate the high degree vertices.
\item Come up with a triangulation which enforces a constant number of
neighbors of triangulation vertices. This has the downside of possibly
creating `long and skinny' triangles which the particle can easily
jump through if the velocity does not have a low enough upper bound.
\item Rely on online techniques to optimize visibility transitions
commonly taken at the cost of space. In the worst case though this
begins to require at least $\Omega(n!)$ space to remember
all possible transitions.
\end{itemize}

The \emph{GetVisPoly} algorithm presented here runs in $O(v)$ time for
$v$ output vertices in the visibility polygon. In practice the completely
visible edge remain unmodified so a more sophisticated algorithm could
run in $O(w)$ for $w$ window vertices in the output visibility polygon.

\subsection{Example Use Case} \label{sec:use-cases}

We have implemented (in a github repository - see~\cite{visibility-github})
a simple app allowing a user to control the motion of a point through a
polygon.

As the basis for an \emph{art-gallery-guard} game, this app would
require low-latency in recomputing the visibility polygon as a guard
moves around the polygon. Our \emph{UpdateVisibility} algorithm becomes
even more applicable when the game becomes multiplayer and the app needs
to compute a visibility polygon for each player.
As the basis for a multi-particle simulation the same logic applies -
we trade off memory usage in favor of constant-time low latency solutions.

