\section{Introduction} \label{sec:intro}

Given effectively unlimited precomputation time, and space we show
that the visibility of a point inside a simple polygon reduces to
(at runtime) the problem of detecting segment intersection with a
much smaller convex polygon. These convex polygons can be further
triangulated to 

Our algorithm is directly applicable to the implementation
of games and simulations involving the continuous motion of points
through a closed and finite partition of a $2$-dimensional space.
For example one might have a particle simulation involving at least
$p \in \Omega(n^2)$ particles ($n$ polygon vertices). In this situation,
the naiive worst case space complexity requires computing $O(n^2)$
distinct visibility polygons each in $O(n)$ time without any
precomputation or memoization optimizations.

Furthermore, many dynamic visibility applications realistically have
the self-imposed limitation of small point velocities. Relatively
low velocities lends itself to lowering the cost of computing the
next segment intersection to cause a \emph{change} in the visibility
polygon. By \emph{change} we mean:

\begin{itemize}
\item A visibility \emph{window} merges with an edge in the polygon
(Figure~\ref{fig:window-edge-merge}).
\item A visibility \emph{window} passes over a vertex in the polygon,
changing which edge it lands on (Figure~\ref{fig:window-vertex-pass}).
\item A \emph{window} is otherwise created or removed / an edge becomes
visibile or invisible (Figure~\ref{fig:edge-change}).
\end{itemize}

All of these cases are defined by our point crossing over an infinite ray
extending from an edge on a reflex vertex, pointing into the polygon
(dashed lines in Figure \ref{fig:visibility-regions}). As we know from the algorithm
for computing the kernel of a polygon, these rays intersect with each
other to form a partitioning of the closed space inside our polygon
into convex subpolygons. In the \emph{Algorithm} section we discuss how
further decomposing these convex subpolygons into Delaunay triangulations
allows us to detect visibility changes in constant time.
% Number of partitions is $\omega(1)$ and $O(n^2)$ convex subpolygons.

